---
title: "Day 5 Session 1"
format: 
  html: 
    code-fold: true
    code-summary: "Show me the code!"
editor: visual
execute:
  echo: true 
  warning: false 
---

## Day 5 Computer Session 1

-   setting warning to false is a cleaner way to show your code -- still read them when you're writing your code, but your audience probably doesn't need to read those messages :)

-   code folding gives your audience an option to hide or reveal the code

    -   done in the top section in html format -- enter, + 2 spaces, enter + 2 spaces:

    title: "Day 5 Session 1"

    format:

    html:

    code-fold: true

    code-summary: "Show me the code!"

    editor: visual

    execute:

    echo: true

    warning: false

-   you can also set options for each chunk of code individually

```{r}
library(tidyverse)
```

## Explore the StarWars data set

```{r}
# look at the first 6 lines
head(starwars)
```

```{r}
# find the dimensions of starwars
dim(starwars) # 87 rows, 14 columns 
```

```{r}
# make a histogram of character heights

ggplot(data = starwars, aes(x = height,
                            fill = gender)) +
  geom_histogram() +
  theme_minimal()
```

```{r}
# make a scatterplot of height vs. weight

ggplot(data = starwars, aes(x = height, 
                            y = mass, 
                            color = sex)) +
  geom_point() +
  theme_minimal()
```

-   using starwars\$height (for example) in console, returns a vector of all height values in our data set

    -   we can see some values are NA

-   in console: class(starwars\$height) returns "integer"

-   

## Calculate Summary Statistics

use mean() function to find means.

use sd() function to find standard deviations.

```{r}
na_mean_height <- mean(starwars$height)

# mean_height returns NA, which is expected
# if you have missing or unknown values in a vector, the default is to say NA because there are unknown values -- use na.rm (rm = remove), set to true or false -- NA values are to be stripped before finding the mean value. default is FALSE (this is why NA was returned)
# other default is to not trim (trim = 0)

```

```{r}
mean_height <- mean(starwars$height, na.rm = TRUE)
mean_height
```

find and store the standard deviation of character heights

```{r}
sd_height <- sd(starwars$height, na.rm = TRUE)
sd_height
```
