---
title: "Day 5 Session 1"
format: 
  html: 
    code-fold: true
    code-summary: "Show me the code!"
editor: visual
execute:
  echo: true 
  warning: false 
---

## Day 5 Computer Session 1

-   setting warning to false is a cleaner way to show your code -- still read them when you're writing your code, but your audience probably doesn't need to read those messages :)

-   code folding gives your audience an option to hide or reveal the code

    -   done in the top section in html format -- enter, + 2 spaces, enter + 2 spaces:

    title: "Day 5 Session 1"

    format:

    html:

    code-fold: true

    code-summary: "Show me the code!"

    editor: visual

    execute:

    echo: true

    warning: false

-   you can also set options for each chunk of code individually

```{r}
library(tidyverse)
```

## Explore the StarWars data set

```{r}
# look at the first 6 lines
head(starwars)
```

```{r}
# find the dimensions of starwars
dim(starwars)
```

```{r}
# make a histogram of character heights

ggplot(data = starwars, aes(x = height)) +
  geom_histogram() +
  theme_minimal()
```

```{r}
# make a scatterplot of height vs. weight

ggplot(data = starwars, aes(x = height, y = mass)) +
  geom_point() +
  theme_minimal()
```
